% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font

\begin{document}

\name{Jonathan K. Petersen}
% \address used twice to have two lines of address
\address{655 N.  Darwin Ave., Logan, UT 84321}
\address{(801) 613-0009}


\begin{resume}

% \section{OBJECTIVE}       A position in the field of computers with special
%                 interests in business applications programming,
%                 information processing, and management systems.


\section{EDUCATION} {\sl Bachelor of Science,} Computer Science \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Utah State University, Logan, UT,
                expected Spring 2016 \\
                Emphases: Information Technology, Science, and Software Development \\
                Minors: Mathematics, Management Information Systems

                {\sl Certificate of Achievement,} Computer Repair and Networking \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Jordan Applied Technology Center, Sandy, UT.
                Graduated Spring 2009 \\

                {\sl High School Diploma} \\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                West Jordan High School, West Jordan, UT,
                Graduated Spring 2009 \\


\section{COMPUTER \\ SKILLS} {\sl Languages \& Software:} C++, Java, PHP, Javascript,
						 Python, Perl, Microsoft Visual Studio, Sublime Text, Eclipse,
						 IntelliJ IDEA. \\
                {\sl Operating Systems:} Microsoft Windows, Apple OSX, Linux (various).

\section{EXPERIENCE} {\sl IT Helpdesk} \hfill Fall 2013 - Current \\
                Information Systems Department, Space Dynamics Laboratory,  \\
                Utah State University Research Foundation, Logan, UT
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Maintained engineering and operational systems to insure resource availability. \\
                 \item Developed automated systems to improve team efficiency.
                \end{itemize}

                {\sl Monitoring Systems Support} \hfill Summer 2013 \\
                Monitoring Team, Riverton Office Building, \\
                The Church of Jesus Christ of Latter-Day Saints, Riverton, UT
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Maintained Monitoring systems to ensure high availability.
                 \item Aided in development of new monitoring systems.
                 \end{itemize}

                {\sl Geek Squad - Counter Intelligence Agent} \hfill Fall 2012 - Spring 2013 \\
                Best Buy, Store 945, Logan, UT
                  \begin{itemize}
                   \item Worked client repairs and ticket system.
                   \item Assisted sales staff with technical sales questions.
                   \end{itemize}

                {\sl Customer Support Specialist.} \hfill Fall 2012 - Spring 2013 \\
                Best Buy, Store 945, Logan, UT
                  \begin{itemize}
                   \item Assisted customers in making smart purchase decisions.
                   \item Maintained a clean and productive store.
                   \end{itemize}

\section{EXTRA-CURRICULAR \\ ACTIVITIES}
            2009 Sterling Scholar - Computer Science \\
            2009 A+ Certified \\
            Geek Squad - Excellent Customer Satisfaction


\end{resume}
\end{document}







